Recovery of deleted deep sequencing data sheds more light on the early Wuhan SARS-CoV-2 epidemic

### 2021-06-17 paper/paper.tex
some formatting

\usepackage[htt]{hyphenat}  % https://tex.stackexchange.com/a/543
\usepackage[export]{adjustbox}
\usepackage{xurl}

@@

\begin{abstract}
The origin and early spread of SARS-CoV-2 remains shrouded in mystery.
Here I identify a data set containing SARS-CoV-2 sequences from early in the Wuhan epidemic that has been deleted from the NIH's Sequence Read Archive.
I recover the deleted files from the Google Cloud, and use them to reconstruct partial sequences of 13 early epidemic viruses.
Phylogenetic analysis of these sequences in the context of carefully annotated existing data suggests that the Huanan Seafood Market sequences that are the focus of the joint WHO-China report are not fully representative of the viruses in Wuhan early in the epidemic.
Instead, the progenitor of currently known SARS-CoV-2 sequences likely contained three mutations relative to the market viruses that made it more similar to SARS-CoV-2's bat coronavirus relatives. 
\end{abstract}

@@

\begin{figure}[]
\centering
\fbox{\includegraphics[trim={0.8in 0.8in 1.1in 1in},clip,width=\linewidth]{figures/pangolin_emails.jpg}}
\caption{Example of the process to delete SRA data.
The image shows e-mails between the lead author of the pangolin coronavirus paper~\citet{xiao2020isolation} and SRA staff excerpted from \citet{USRTK2020}.
}
\label{fig:pangolin_emails}
\end{figure}

@@

@@

\begin{table*}[]
{\small
\begin{tabular}{lrll}
\toprule
sample &  fraction sites called (21570-29550) &           patient group &                                        substitutions relative to proCoV2 \\
\midrule
A4 &                               0.9827 &        early outpatient &                                                                          none \\
C1 &                               0.9966 &        early outpatient &  G22081A (A=924, C=4, G=9), C28144T (C=6, T=1185), T29483G (C=1, G=45, T=1) \\
C2 &                               0.9962 &        early outpatient &                                                 C29095T (C=1, G=1, T=751)  \\
C9 &                               0.9536 &        early outpatient &                                  C28144T (C=3, T=823), G28514T (G=1, T=36)  \\
D9 &                               0.9585 &        early outpatient &                                                     C28144T (C=4, T=1653)  \\
D12 &                               0.9970 &        early outpatient &                                                     C28144T (C=8, T=2400)  \\
E1 &                               0.9759 &        early outpatient &                                                           C28144T (T=125)  \\
E5 &                               0.9758 &        early outpatient &              C24034T (A=5, C=3, T=74), T26729C (C=12), G28077C (C=142, G=4)  \\
E11 &                               0.9877 &        early outpatient &                                 C25460T (C=2, T=246), C28144T (C=1, T=412)  \\
F11 &                               0.9594 &        early outpatient &                             T25304A (A=9, T=1), C28144T (C=6, G=1, T=1328)  \\
G1 &                               0.9959 &        early outpatient &                                   none                                        \\
G11 &                               0.9677 &        early outpatient &                                  none                                         \\
H9 &                               0.9941 &        early outpatient &                                                     C28144T (C=2, T=1254)  \\
R11 &                               0.9987 &  hospital patient (Feb) &                               C21707T (T=401), C28144T (A=1, C=18, T=4265)  \\
\bottomrule
\end{tabular}
}
\caption{Samples for which the SARS-CoV-2 sequence could be called at $\ge$95\% of sites between 21,570 and 29,550, and the substitutions in this region relative to the putative SARS-CoV-2 progenitor proCoV2 inferred by \citet{kumar2021evolutionary}.
Numbers in parentheses after each substitution give the deep sequencing reads with each nucleotide identity.
\label{tab:mutations}
}
\end{table*}

>>>>

\usepackage[htt]{hyphenat}  % https://tex.stackexchange.com/a/543
\usepackage[export]{adjustbox}
\usepackage{xurl}
\usepackage{stfloats}

\renewcommand{\topfraction}{0.9}	% max fraction of floats at top
    \renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
    %   Parameters for TEXT pages (not float pages):
    \setcounter{topnumber}{2}
    \setcounter{bottomnumber}{2}
    \setcounter{totalnumber}{4}     % 2 may work better
    \setcounter{dbltopnumber}{2}    % for 2-column pages
    \renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
    \renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
    %   Parameters for FLOAT pages (not text pages):
    \renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
	% N.B.: floatpagefraction MUST be less than topfraction !!
    \renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages

@@

\begin{abstract}
The origin and early spread of SARS-CoV-2 remains shrouded in mystery.
Here I identify a data set containing SARS-CoV-2 sequences from early in the Wuhan epidemic that has been deleted from the NIH's Sequence Read Archive.
I recover the deleted files from the Google Cloud, and reconstruct partial sequences of 13 early epidemic viruses.
Phylogenetic analysis of these sequences in the context of carefully annotated existing data suggests that the Huanan Seafood Market sequences that are the focus of the joint WHO-China report are not fully representative of the viruses in Wuhan early in the epidemic.
Instead, the progenitor of known SARS-CoV-2 sequences likely contained three mutations relative to the market viruses that made it more similar to SARS-CoV-2's bat coronavirus relatives. 
\end{abstract}

@@

\begin{figure}[]
\centering
\fbox{\includegraphics[trim={0in 0in 0in 0in},clip,width=\linewidth]{figures/pangolin_emails.jpg}}
\caption{Example of the process to delete SRA data.
The image shows e-mails between the lead author of the pangolin coronavirus paper~\citet{xiao2020isolation} and SRA staff excerpted from \citet{USRTK2020}.
}
\label{fig:pangolin_emails}
\end{figure}

@@

\begin{table*}[b!]
{\small
\begin{tabular}{lrll}
\toprule
sample &  fraction sites called (21570-29550) &           patient group &                                        substitutions relative to proCoV2 \\
\midrule
A4 &                               0.9827 &        early outpatient &                                                                          none \\
C1 &                               0.9966 &        early outpatient &  G22081A (A=924, C=4, G=9), C28144T (C=6, T=1185), T29483G (C=1, G=45, T=1) \\
C2 &                               0.9962 &        early outpatient &                                                 C29095T (C=1, G=1, T=751)  \\
C9 &                               0.9536 &        early outpatient &                                  C28144T (C=3, T=823), G28514T (G=1, T=36)  \\
D9 &                               0.9585 &        early outpatient &                                                     C28144T (C=4, T=1653)  \\
D12 &                               0.9970 &        early outpatient &                                                     C28144T (C=8, T=2400)  \\
E1 &                               0.9759 &        early outpatient &                                                           C28144T (T=125)  \\
E5 &                               0.9758 &        early outpatient &              C24034T (A=5, C=3, T=74), T26729C (C=12), G28077C (C=142, G=4)  \\
E11 &                               0.9877 &        early outpatient &                                 C25460T (C=2, T=246), C28144T (C=1, T=412)  \\
F11 &                               0.9594 &        early outpatient &                             T25304A (A=9, T=1), C28144T (C=6, G=1, T=1328)  \\
G1 &                               0.9959 &        early outpatient &                                   none                                        \\
G11 &                               0.9677 &        early outpatient &                                  none                                         \\
H9 &                               0.9941 &        early outpatient &                                                     C28144T (C=2, T=1254)  \\
R11 &                               0.9987 &  hospital patient (Feb) &                               C21707T (T=401), C28144T (A=1, C=18, T=4265)  \\
\bottomrule
\end{tabular}
}
\caption{Samples for which the SARS-CoV-2 sequence could be called at $\ge$95\% of sites between 21,570 and 29,550, and the substitutions in this region relative to the putative SARS-CoV-2 progenitor proCoV2 inferred by \citet{kumar2021evolutionary}.
Numbers in parentheses after each substitution give the deep sequencing reads with each nucleotide identity.
\label{tab:mutations}
}
\end{table*}

@@
